Unshuffling Permutations

### 2015-09-24 submission.tex
typos

We follow the usual terminology on words~\cite{ChoffrutKarhumaki1997}.
Let us recall here the most important ones. Let $u$ be a word. The
length of $u$ is denoted by $|u|$. The {\em empty word}, the only word
of null length, is denoted by $\epsilon$. We denote by $\widetilde{u}$
the {\em mirror image} of $u$ that is the word
$u_{|u|} u_{|u| - 1} \dots u_1$. If $P$ is a subset of $[|u|]$, $u_{|P}$
is the subword of $u$ consisting in the letters of $u$ at the positions
specified by the elements of $P$. If $u$ is a word of integers and $k$
is an integer, we denote by $u[k]$ the word obtained by incrementing by
$k$ all letters of $u$. The {\em shuffle} of two words $u$ and $v$ is
the set recursively defined by
$u \shuffle \epsilon = u = \epsilon \shuffle u$ and
$ua \shuffle vb = (u \shuffle vb)a \cup (ua \shuffle v)b$, were $a$ and
$b$ are letters. A word $u$ is a {\em square} if there exists a word $v$
such that $u$ belongs to $v \shuffle v$.

We denote by $S_n$ the set of permutations of size $n$ and by $S$ the
set of all permutations. In this paper, permutations of a size $n$ are
specified by words of length $n$ on the alphabet $[n]$ and without
multiple occurrence of a letter, so that all above definitions about
words remain valid on permutations. The only difference lies on the
fact that we shall denote by $\pi(i)$ (instead of $\pi_i$) the $i$-th
letter of any permutation $\pi$. For any nonnegative integer $n$, we
write $\nearrow_{n}$ (resp. $\searrow_{n}$) for the permutation
$1 2 \dots n$ (resp. $n (n-1) \dots 1$). If $\pi$ is a permutation of
$S_n$, we denote by $\bar \pi$ the {\em complementary} of $\pi$ that is
the permutation satisfying $\bar \pi(i) = n - \pi(i) + 1$ for all
$i \in [n]$. The {\em inverse} of $\pi$ is denoted by $\pi^{-1}$.

>>>>

We follow the usual terminology on words~\cite{ChoffrutKarhumaki1997}.
Let us recall here the most important ones. Let $u$ be a word. The
length of $u$ is denoted by $|u|$. The {\em empty word}, the only word
of null length, is denoted by $\epsilon$. We denote by $\widetilde{u}$
the {\em mirror image} of $u$, that is the word
$u_{|u|} u_{|u| - 1} \dots u_1$. If $P$ is a subset of $[|u|]$, $u_{|P}$
is the subword of $u$ consisting in the letters of $u$ at the positions
specified by the elements of $P$. If $u$ is a word of integers and $k$
is an integer, we denote by $u[k]$ the word obtained by incrementing by
$k$ all letters of $u$. The {\em shuffle} of two words $u$ and $v$ is
the set recursively defined by
$u \shuffle \epsilon = u = \epsilon \shuffle u$ and
$ua \shuffle vb = (u \shuffle vb)a \cup (ua \shuffle v)b$, were $a$ and
$b$ are letters. A word $u$ is a {\em square} if there exists a word $v$
such that $u$ belongs to $v \shuffle v$.

We denote by $S_n$ the set of permutations of size $n$ and by $S$ the
set of all permutations. In this paper, permutations of a size $n$ are
specified by words of length $n$ on the alphabet $[n]$ and without
multiple occurrence of a letter, so that all above definitions about
words remain valid on permutations. The only difference lies on the
fact that we shall denote by $\pi(i)$ (instead of $\pi_i$) the $i$-th
letter of any permutation $\pi$. For any nonnegative integer $n$, we
write $\nearrow_{n}$ (resp. $\searrow_{n}$) for the permutation
$1 2 \dots n$ (resp. $n (n-1) \dots 1$). If $\pi$ is a permutation of
$S_n$, we denote by $\bar \pi$ the {\em complementary} of $\pi$, that is
the permutation satisfying $\bar \pi(i) = n - \pi(i) + 1$ for all
$i \in [n]$. The {\em inverse} of $\pi$ is denoted by $\pi^{-1}$.
